Let $1 \leq p < \infty$ and $1 \leq q \leq \infty$ and $s \in \R$, we define the \emph{homogeneous Triebel-Lizorkin space} $\dot F^{s, p}_q (\R^d)$ as the completion of $\cS (\R^d)$ with respect to the norm 
	\[ ||u||_{\dot F^{s, p}_q} := \left|\left| || N^s u_N ||_{\ell^q_N} \right|\right|_{L^p_x} = \left|\left| \left( \sum_{N \in 2^\Z} |N^s u_N|^q \right)^{1/q} \right|\right|_{L^p}. \]	
For the same range of exponents, we analogously define the \emph{inhomogeneous Triebel-Lizorkin space} $F^{s, p}_q (\R^d)$ as the completion of $\cS (\R^d)$ with respect to the norm 	
	\[ ||u||_{F^{s, p}_q} := \left|\left| || \langle N\rangle ^s u_N ||_{\ell^q_N} \right|\right|_{L^p_x} = ||u_{\leq 1}||_{L^p} + \left|\left| \left( \sum_{N \in 2^\N} |N^s u_N|^q \right)^{1/q} \right|\right|_{L^p} \]	

\subsection{Properties}
We can read off some basic properties of Triebel-Lizorkin spaces from the definitions and properties of $L^p$-spaces and $\ell^q$-spaces. 

\begin{proposition}[Mononoticity in $q$ and $s$]
	Let $1 \leq p \leq \infty$ and $s \in \R$. 
\begin{enumerate}
	\item For $1 \leq q_1 \leq q_2 \leq \infty$, we have
			\begin{align*}
				||u||_{F^{s, p}_{q_2}} 
					&\lesssim_{q_1, q_2} ||u||_{F^{s, p}_{q_1}},\\
				||u||_{\dot F^{s, p}_{q_2}} 
					&\lesssim_{q_1, q_2} ||u||_{\dot F^{s, p}_{q_1}}.
			\end{align*}
		In particular, we have the continuous embeddings $F^{s, p}_{q_1} (\R^d) \hookrightarrow F^{s, p}_{q_2} (\R^d)$ and $\dot F^{s, p}_{q_1} (\R^d) \hookrightarrow \dot F^{s, p}_{q_2} (\R^d)$. 
	
	\item For $1 \leq q_1, q_2 \leq \infty$ and $\alpha > 0$, we have
			\begin{align*}
				||u||_{F^{s, p}_{q_2}} \lesssim_\alpha ||u||_{F^{s + \alpha, p}_{q_1}}.
			\end{align*}
		In particular, we have the continuous embedding $B^{s + \alpha, p}_{q_1} (\R^d) \hookrightarrow B^{s, p}_{q_2} (\R^d)$.
\end{enumerate}\label{prop:basicembedtriebel}	
\end{proposition}

\begin{proof}
\leavevmode
\begin{enumerate}
	\item This follows immediately from the embedding $\ell^{q_1} \hookrightarrow \ell^{q_2}$ and the definition of the Triebel-Lizorkin norms. 
	
	\item By (a), it suffices to prove the result for $q_1 = \infty$ and $q_2 = 1$. We can write
		\begin{align*}
			\sum_{N \in 2^\N} |N^s u_N| \leq \Big|\Big| N^{s + \alpha} |u_N| \Big|\Big|_{\ell^\infty_N (2^\N)} \sum_{N \in 2^\N} N^{-\alpha} \lesssim \Big|\Big| N^{s + \alpha} |u_N| \Big|\Big|_{\ell^\infty_N (2^\N)}.
		\end{align*}
		Taking the $L^p$-norm of both sides, we conclude the result. 
\end{enumerate}
\end{proof}

\begin{proposition}[Lifting property]
	Let $1 \leq p < \infty$ and $1 \leq q \leq \infty$ and $s, \sigma \in \R$. Then 
		\begin{align*}
			|||\nabla|^\sigma u||_{\dot F^{s - \sigma, p}_q}
				&\sim ||u||_{\dot F^{s, p}_q}\\
			 || \langle \nabla \rangle^\sigma u ||_{F^{s - \sigma, p}_q} 
			 	&\sim ||u||_{B^{s, p}_q} ,
		\end{align*}	 
	That is, $|\nabla|^\sigma : 	\dot F^{s - \sigma, p}_q (\R^d) \to \dot F^{s, p}_q (\R^d)$ and $\langle \nabla \rangle^\sigma : 	F^{s - \sigma, p}_q (\R^d) \to F^{s, p}_q (\R^d)$ isomorphically. 
\end{proposition}

\begin{proof}
	Maximal function argument. 
\end{proof}

The expected duality relations hold for Triebel-Lizorkin spaces; the proofs are essentially identical to that for Lebesgue spaces and Sobolev spaces.

\begin{theorem}[Duality]
	Let $1 \leq p < \infty$ and $1 < q < \infty$ and $s \in \R$, then 
		\begin{align*}
			\dot F^{s, p}_{q} (\R^d)^* 
				&\cong \dot F^{-s, p'}_{q'} (\R^d), \\
			F^{s, p}_{q} (\R^d)^* 
				&\cong  F^{-s, p'}_{q'} (\R^d).
		\end{align*}
\end{theorem}

\begin{proof}\cite[Theorem 2.11.2]{Triebel1983}
	The inclusion $\dot F^{-s, p'}_{q'} (\R^d) \hookrightarrow \dot F^{s, p}_{q} (\R^d)^* $ is essentially Holder's inequality while the reverse inclusion follows from the identification $\ell^q L^p (2^\Z \times \R^d)^* \cong \ell^{q'} L^{p'} (2^\Z \times \R^d)$ and Hahn-Banach. 
\end{proof}

\subsection{Embeddings}

As the Triebel-Lizorkin norm is defined by first summing pointwise, we cannot easily apply Bernstein's inequality as we did in the case of the Besov embedding inequalities. Instead, we will rely on an interpolation argument due to \cite{BrezisMironescu2001}. 

\begin{theorem}[Homogeneous Triebel-Lizorkin embedding]
	Let $1 \leq p_1 < p_2 < \infty$ and $1 \leq q_1, q_2 \leq \infty$ and $s_2 < s_1$, then
		\[ || u ||_{\dot F^{s_2, p_2}_{q_2}} \lesssim || u ||_{\dot F^{s_1, p_1}_{q_1}} \]
	whenever $\frac{s_1}{d} - \frac{1}{p_1} = \frac{s_2}{d} - \frac{1}{p_2}$. In particular, we have the continuous embedding $\dot F^{s_1, p_1}_{q_1} (\R^d) \hookrightarrow \dot F^{s_2, p_2}_{q_2} (\R^d)$.
\end{theorem}

\begin{proof}
	By Proposition \ref{prop:basicembedtriebel} (a), it suffices to consider the case $q_1 = \infty$ and $q_2 = 1$. We argue by interpolating the $\dot F^{s_2, p_2}_1$-norm between the $\dot B^{s_1, \infty}_\infty$-norm and $\dot F^{s_1, p_1}_\infty$-norm. Set $s_0 := s_1 - \tfrac{d}{p_1} = s_2 - \tfrac{d}{p_2}$, then $s_2 = s_\theta$ is the interpolation exponent between $s_0$ and $s_1$ for $\theta = \tfrac{p_1}{p_2}$, i.e. $(1 - \theta) s_0 + \theta s_1 = s_2$. We control each Littlewood-Paley projection pointwise depending on whether it is high frequency or low frequency, 	
		\[ |u_N| \leq \min \left\{ N^{-s_0} \Big|\Big| A^{s_0} |u_A| \Big| \Big|_{\ell^\infty_A (2^\Z)} , N^{-s_1} \Big|\Big| B^{s_1} |u_B| \Big| \Big|_{\ell^\infty_B (2^\Z)}\right\}\]
	where the transition occurs when $M^{-s_0} \Big|\Big| A^{s_0} |u_A| \Big| \Big|_{\ell^\infty_A (2^\Z)} \sim M^{-s_1} \Big|\Big| B^{s_1} |u_B| \Big| \Big|_{\ell^\infty_B (2^\Z)}$. We can therefore write
		\begin{align*}
			\sum_{N \in 2^\Z} N^{s_2} |u_N(x)| 
				&\lesssim \sum_{N \in 2^\Z} N^{s_2} \min \left\{ N^{-s_0} \Big|\Big| A^{s_0} |u_A| \Big| \Big|_{\ell^\infty_A (2^\Z)} , N^{-s_1} \Big|\Big| B^{s_1} |u_B| \Big| \Big|_{\ell^\infty_B (2^\Z)}\right\} \\
				&\leq  \Big|\Big| A^{s_0} |u_A| \Big| \Big|_{\ell^\infty_A (2^\Z)}\sum_{N \lesssim M} N^{s_2 -s_0} 		
				 + \Big|\Big| B^{s_1} |u_B| \Big| \Big|_{\ell^\infty_B (2^\Z)}\sum_{N \gtrsim M} N^{s_2 -s_1} 
				\\
				&\lesssim \Big|\Big| A^{s_0} |u_A| \Big| \Big|_{\ell^\infty_A (2^\Z)} M^{s_2 -s_0} 		
				 + \Big|\Big| B^{s_1} |u_B| \Big| \Big|_{\ell^\infty_B (2^\Z)} M^{s_2 -s_1} 
				\\
				&\lesssim  \Big|\Big| A^{s_0} |u_A| \Big| \Big|_{\ell^\infty_A (2^\Z)} \left( \frac{\Big|\Big| B^{s_1} |u_B| \Big| \Big|_{\ell^\infty_B (2^\Z)}}{\Big|\Big| A^{s_0} |u_A| \Big| \Big|_{\ell^\infty_A (2^\Z)}} \right)^{\frac{s_2 - s_0}{s_1 - s_0}} + \Big|\Big| B^{s_1} |u_B| \Big| \Big|_{\ell^\infty_B (2^\Z)} \left( \frac{\Big|\Big| B^{s_1} |u_B| \Big| \Big|_{\ell^\infty_B (2^\Z)}}{\Big|\Big| A^{s_0} |u_A| \Big| \Big|_{\ell^\infty_A (2^\Z)}} \right)^{\frac{s_2 - s_1}{s_1 - s_0}} \\
				&\lesssim \Big|\Big| A^{s_0} |u_A| \Big| \Big|_{\ell^\infty_A (2^\Z)}^{1 - \theta} \Big|\Big| B^{s_1} |u_B| \Big| \Big|_{\ell^\infty_B (2^\Z)}^\theta.
		\end{align*}	
	Taking the $L^{p_2}$-norm of both sides and applying Holder, we obtain 
		\[ ||u||_{\dot F^{s_2, p_2}_1} \lesssim  \Big|\Big| A^{s_0} ||u_A||_{L^\infty_x} \Big| \Big|_{\ell^\infty_A (2^\Z)}^{1 - \theta} \left|\left|\Big|\Big| B^{s_1} |u_B| \Big| \Big|_{\ell^\infty_B (2^\Z)}^\theta \right|\right|_{L^{p_2}_x}. \]
	By definition $\theta p_2 = p_1$, so the second term on the right can be written as the $\dot F^{s_1, p_1}_\infty$-norm. The first term on the right is the $\dot B^{s_1, \infty}_\infty$-norm which is controlled by the $\dot F^{s_1, p_1}_\infty$-norm via Bernstein's inequality, 
		\[  \Big|\Big| A^{s_0} ||u_A||_{L^\infty_x} \Big| \Big|_{\ell^\infty_A (2^\Z)} \lesssim  \Big|\Big| A^{s_1} ||u_A||_{L^{p_1}} \Big| \Big|_{\ell^\infty_A (2^\Z)} \leq ||u||_{\dot F^{s_1, p_1}_\infty}. \]	
	This completes the proof. 
\end{proof}		


\begin{theorem}[Inhomogeneous Triebel-Lizorkin embedding]
	Let $1 \leq p_1 < p_2 < \infty$ and $1 \leq q_1, q_2 \leq \infty$ and $s_2 < s_1$, then 
		\[ || u ||_{F^{s_2, p_2}_{q_2}} \lesssim || u ||_{F^{s_1, p_1}_{q_1}} \]
	whenever $\frac{s_1}{d} - \frac{1}{p_1} \geq \frac{s_2}{d} - \frac{1}{p_2}$. In particular, we have the continuous embedding $F^{s_1, p_1}_{q_1} (\R^d) \hookrightarrow F^{s_2, p_2}_{q_2} (\R^d)$.
\end{theorem}

\begin{proof}
	By Proposition \ref{prop:basicembedtriebel} (a), it suffices to consider the case $q_1 = \infty$ and $q_2 = 1$, and by (b) we can assume without loss of generality the critical exponents $\frac{s_1}{d} - \frac{1}{p_1} = \frac{s_2}{d} - \frac{1}{p_2}$. Control over the low frequency term $u_{\leq 1}$ follows from Bernstein's inequality. For the high frequency terms $N \in 2^\N$, mimicking the proof of the homogeneous embedding inequality furnishes the result. 
\end{proof}

\begin{remark}
	Comparing with the Besov embedding inequalities, note the Triebel-Lizorking embeddings do not have the restriction $q_1 \leq q_2$ on the range of summability indices. 
\end{remark}

\subsection{Traces}

As with the embedding inequalities, studying the properties of the trace operator on Triebel-Lizorkin spaces is more complicated than that of Besov spaces. For conciseness of presentation, we will only consider the sub-critical problem. 

\begin{theorem}[Triebel-Lizorkin trace theorem]
	Let $1 < p < \infty$ and $1 \leq q \leq \infty$ and $s > \sigma > \tfrac1p$, then the trace map satisfies
		\[ ||Tu||_{B^{s - \sigma, p}_p (\R^{d - 1})} \lesssim ||u||_{F^{s, p}_q (\R^d)}. \]
	In particular, it extends to a bounded linear operator $T: 	F^{s, p}_q (\R^d) \to B^{s - \sigma, p}_p (\R^{d - 1})$.
\end{theorem}

\begin{proof}
	It suffices by Proposition \ref{prop:basicembedtriebel} (a) to prove the result for $q = \infty$. We perform a Littlewood-Paley decomposition $u = \sum_N P_N u$. By linearity, we can write $P'_M T u = \sum_N P'_M T P_N u$. Applying the triangle inequality, the previous two lemmas, and boundedness of the projections, we estimate
		\begin{align*}
			||P'_M Tu||_{L^p (\R^{d-1}_{x'})}
				&\lesssim  \sum_{N : M \lesssim N} ||P'_M T P_N u||_{L^p (\R^{d - 1}_{x'})}\\
				&\lesssim \sum_{N : M \lesssim N} N^{\frac1p} ||P_N u||_{L^p (\R^d_x)}.
		\end{align*}		
	Multiplying both sides by $M^{s- \sigma}$ and taking $\ell^p$-norms, we get
		\begin{align*}
			\Big|\Big|  ||M^{s - \sigma} P_M T u||_{L^p (\R^d_x)}\Big|\Big|_{\ell^p_M (2^\N)}
			 	&\lesssim \left|\left| M^{s - \sigma} \sum_{N : M \lesssim N} N^{1/p} ||P_N u||_{L^p (\R^d_x)}\right|\right|_{\ell^p_M (2^\N)} \\
			 	&\lesssim \left|\left| \sum_{N : M \lesssim N} M^{s - \sigma} N^{\frac1p -s} \right|\right|_{\ell^p_M (2^\N)} \Big|\Big|  || N^s P_N u ||_{\ell^\infty_N} \Big|\Big|_{L^p_x} \lesssim \Big|\Big| ||N^{s} P_N u||_{\ell^\infty_N} \Big|\Big|_{L^p_x}
		\end{align*}	 
	This completes the proof. 
\end{proof}

\begin{remark}
	The trace theorem also holds for the critical exponent $\sigma = \frac1p$ and endpoints $p = 1, \infty$. Furthermore, the extension operator as defined in Theorem \ref{thm:besovext} admits the desired boundedness properties. See \cite[Theorem 2.7.2]{Triebel1983} for details. 
\end{remark}

\subsection{Example: Sobolev spaces}

The most familiar examples of Triebel-Lizorkin spaces are the Lebesgue spaces $L^p (\R^d)$ and the Sobolev spaces $W^{s, p} (\R^d)$. Let $1 < p < \infty$ and $s \in \R$, we define the \emph{homogeneous Sobolev space}, also known as the Riesz potential space, $\dot W^{s, p} (\R^d)$, as the completion of the homogeneous Schwartz space $\dot \cS (\R^d)$ with respect to the norm 
	\[ ||u||_{\dot W^{s, p}} := |||\nabla|^s u||_{L^p}. \]
Analogously, we define the \emph{inhomogeneous Sobolev space}, also known as the Bessel potential space, $W^{s, p} (\R^d)$, as the closure of Schwartz space $\cS (\R^d)$ with respect to the norm 
	\[ ||u||_{W^{k, p}} := ||\langle \nabla \rangle^s u||_{L^p}. \]
The realisations of these spaces on the Triebel-Lizorkin scale of function spaces follows from the \textit{almost orthogonality} of the projection operators in form of the Littlewood-Paley square function estimate. 	

\begin{lemma}[Littlewood-Paley square function estimate]
\label{thm:square}
	For $1 < p < \infty$, we have
		\[ || u||_{L^p} \sim  \Big|\Big| \Big( \sum_{N \in 2^\Z} N^{2s} |u_N|^2 \Big)^\frac12 \Big|\Big|_{L^p}. \]
	In particular, $L^p (\R^d) = \dot F^{0, p}_2 (\R^d) = F^{0, p}_2 (\R^d)$. 	
\end{lemma}

\begin{proof}
	We refer the interested reader to \cite[Chapter IV]{Stein1970} or \cite[Theorem 8.4]{Duoandikoetxea2001}. 
\end{proof}

\begin{remark}
	The estimate fails at the endpoints. For $p = \infty$, taking $f = 1$, we have $f_N = 0$ and therefore $S(f) = 0$. For $p = 1$, take $f = \phi_\epsilon$ where $\{\phi_\epsilon\}_\epsilon \subseteq C^\infty_c (\R^d)$ is an approximation to the identity. 
\end{remark}

\begin{theorem}[Triebel-Lizorkin characterisation of Sobolev spaces]
	Let $1 < p < \infty$ and $s \in \R$, then 
		\begin{align*}
			 || u ||_{\dot W^{s, p}} 
			 	&\sim ||u||_{\dot F^{s, p}_2},\\
			 || u ||_{W^{s, p}} 
			 	&\sim ||u||_{F^{s, p}_2}.
		\end{align*}	 
	In particular, $\dot W^{s, p} (\R^d) = \dot F^{s, p}_2 (\R^d)$ and $W^{s, p} (\R^d) = F^{s, p}_2 (\R^d)$. 
\end{theorem}

\begin{proof}	 	
	We prove the homogeneous case, leaving the inhomogeneous case as an exercise. The symbol of the Littlewood-Paley projections $P_N = \psi_N (\nabla)$ is a smooth cut-off $\psi_N \in C^\infty_c (\R^d - 0)$. Note that the square function estimate continues to hold replacing it with any other smooth cut-off $\chi \in C^\infty_c (\R^d - 0)$, for example
		\[ \chi (\xi) = |\xi|^{-s} \psi(\xi), \qquad \chi_N (\xi) = \chi(\xi/N) = N^s \psi_N (\xi) |\xi|^{-s}. \]
	Observe that $\widecheck{\chi_N} * g = N^s P_N |\nabla|^{-s} g$. Taking $g = |\nabla|^s u$, it follows from the square function estimate that
		\[ \Big|\Big| \Big( \sum_{N \in 2^\Z} N^{2s} |u_N|^2 \Big)^\frac12 \Big|\Big|_{L^p} \lesssim |||\nabla|^s u||_{L^p}. \]	
	For the converse, we argue by duality and the direction above;
	\begin{align*}
		|||\nabla|^s u||_{L^p}
			&= \sup_{||g||_{L^{p'}} = 1} \langle |\nabla|^s u, g \rangle = \sup_{||g||_{L^{p'}} = 1} \sum_{N \in 2^\Z} \langle \widetilde{P_N} P_N |\nabla|^s u, g \rangle = \sup_{||g||_{L^{p'}} = 1} \sum_{N \in 2^\Z} \langle N^s P_N |\nabla|^s u,  N^{-s} \widetilde{P_N} g \rangle \\
			&\leq  \sup_{||g||_{L^{p'}} = 1} \int_{\R^d} \Big( \sum_{N \in 2^\Z} N^{2s} |u_N|^2 \Big)^{\frac12} \Big( \sum_{N \in 2^\Z} N^{-2s} |\widetilde{P_N} |\nabla|^s g|^2 \Big)^{\frac12} \, dx \\
			&\leq  \sup_{||g||_{L^{p'}} = 1} \Big| \Big| \Big( \sum_{N \in 2^\Z} N^{2s} |u_N|^2 \Big)^{\frac12}\Big|\Big|_{L^p} \Big| \Big|  \Big( \sum_{N \in 2^\Z} N^{-2s} |\widetilde{P_N} |\nabla|^s g|^2 \Big)^{\frac12} \Big|\Big|_{L^{p'}} \lesssim  \Big| \Big| \Big( \sum_{N \in 2^\Z} N^{2s} |u_N|^2 \Big)^{\frac12}\Big|\Big|_{L^p},
	\end{align*}
	where the first line we use self-adjointness, the second line follows from Cauchy-Schwartz, the third line follows from Holder's inequality. 
\end{proof}	