The Sobolev embedding inequalities trade regularity for integrability. The general strategy will be to prove the embedding inequality for each Littlewood-Paley projection, and then efficiently sum by using Bernstein's inequality to recover the original result,
	\begin{align*}
		||u||_{L^q}
			\leq \sum_{N \in 2^\Z} ||u_N||_{L^q} \lesssim \sum_{N \in 2^\Z} N^{\frac{d}{p} - \frac{d}{q}} ||u_N||_{L^p},
	\end{align*}
for $1 \leq p < q \leq \infty$. The factor $N^{\frac{d}{p} - \frac{d}{q}}$ decays for $N \lesssim 1$, so we can control low frequencies by a lower order term. The factor instead grows for $N \gtrsim 1$, so we need to control high frequencies by a higher order term via the \textit{Sobolev-Bernstein} inequality to recover decay. 

\subsection{$L^p$-inequalities}

When localising to frequencies $|\xi| \sim N$, the Riesz potentials behave like $|\nabla|^s \sim N^s$, while the Bessel potentials behave like $\langle \nabla \rangle^s \sim \langle N \rangle^s$. The heuristic is that positive-order differential operators $s > 0$ accentuate high frequencies and diminish low frequencies, while negative-order operators have the opposite effect. More precisely, we have the following family of inequalities, 


\begin{lemma}[Sobolev-Bernstein inequalities] For $f \in L^p (\R^d)$, 
				\begin{alignat*}{2}
					|| |\nabla|^s u_N||_{L^p} 
						&\sim N^s ||u_N||_{L^p}, &&\qquad \text{if }s \in \R \text{ and } 1 \leq p \leq \infty, \\
					|| |\nabla|^s u_{\leq N}||_{L^p} 
						&\lesssim N^s ||u_{\leq N}||_{L^p}, &&\qquad\text{if }s > 0 \text{ and } 1 \leq p < \infty, \\
					|| |\nabla|^s u_{\geq N}||_{L^p} 
						&\lesssim N^s ||u_{\geq N}||_{L^p}, &&\qquad\text{if }s < 0 \text{ and } 1 \leq p < \infty.
				\end{alignat*}			
		The endpoint cases $p = \infty$ for the latter two inequalities hold for $u \in \cS (\R^d)$. 
\end{lemma}



\begin{theorem}[Gagliardo-Nirenberg inequality]
	Let $1 < p < q \leq \infty$ and $s > 0$, then 
		\[ ||u||_{L^q} \lesssim ||u||_{L^p}^{1 - \theta} || |\nabla|^s u ||_{L^p}^\theta \]
	where $0 < \theta < 1$ satisfies $\tfrac1p - \tfrac1q = \tfrac{\theta s}{d}$. 	
\end{theorem}

\begin{proof}
	Taking a Littlewood-Paley decomposition $u = \sum_N u_N$, we apply the triangle inequality and Bernstein's inequality to obtain
	\begin{align*}
		||u||_{L^q}
			\leq \sum_{N \in 2^\Z} ||u_N||_{L^q} \lesssim \sum_{N \in 2^\Z} N^{\theta s} ||u_N||_{L^p}.
	\end{align*}
	Boundedness of the Littlewood-Paley projections and the Sobolev-Bernstein inequality give the respective bounds
		\[ ||u_N||_{L^p} \lesssim ||u||_{L^p}, \qquad ||u_N||_{L^p} \lesssim N^{-s} || |\nabla|^s u||_{L^p}.\]
	Hence
		\[ ||u_N||_{L^p} \lesssim \min \Big\{ ||u||_{L^p}, N^{-s} || |\nabla|^s u||_{L^p} \Big\}. \]
	Decomposing the sum at the transition $N \sim (|||\nabla|^s u||_{L^p}/||u||_{L^p})^{1/s}$ into high and low frequencies, we conclude
		\begin{align*}
			||u||_{L^q}
				&\lesssim \Big( \sum_{N \lesssim (|||\nabla|^s u||_{L^p}/||u||_{L^p})^{1/s}} + \sum_{N \gtrsim (|||\nabla|^s u||_{L^p}/||u||_{L^p})^{1/s}} \Big) N^{\theta s} ||u_N||_{L^p} \\
				&\lesssim \sum_{N \lesssim (|||\nabla|^s u||_{L^p}/||u||_{L^p})^{1/s}} N^{\theta s} ||u||_{L^p} + \sum_{N \gtrsim (|||\nabla|^s u||_{L^p}/||u||_{L^p})^{1/s}} N^{(\theta - 1) s}  |||\nabla|^s u||_{L^p} \lesssim ||u||_{L^p}^{1 - \theta} || |\nabla|^s u||_{L^p}^\theta 
		\end{align*}	
	as desired. 	
\end{proof}

\begin{theorem}[Non-endpoint Sobolev inequality]
	Let $1 \leq p < q \leq \infty$, and suppose $u \in \cS (\R^d)$ then 
		\[ ||u||_{L^q} \lesssim || \langle \nabla \rangle^s u ||_{L^p} \]
	whenever $\tfrac1p - \tfrac1q < \tfrac{s}{d}$ and $s > 0$. In particular, $W^{s, p} (\R^d) \subseteq L^q (\R^d)$ and, in the endpoint case $q = \infty$ and $\tfrac1p < \tfrac{s}{d}$, we have $W^{s, p} (\R^d) \subseteq C^0 (\R^d)$. 
\end{theorem}

\begin{proof}
	Taking a Littlewood-Paley decomposition $u = \sum_N u_N$, we apply the triangle inequality and Bernstein's inequality to obtain
		\[ ||u||_{L^q} \leq \sum_{N \in 2^\Z} ||u_N||_{L^q} \lesssim \sum_{N \in 2^\Z} N^{\frac{d}{p} - \frac{d}{q}} ||u_N||_{L^p}. \]
	Boundedness of the Littlewood-Paley projections and the Sobolev-Bernstein inequality give the respective bounds	
		\[ ||u_N||_{L^p} \lesssim ||u||_{L^p} \lesssim || \langle \nabla \rangle^s u||_{L^p}, \qquad ||u_N||_{L^p} \sim N^{-s} |||\nabla|^s u||_{L^p}\lesssim N^{-s} || \langle \nabla \rangle^s u||_{L^p}. \]
	Hence
		\[ ||u_N||_{L^p} \lesssim \min\{ 1, N^{-s} \} || \langle \nabla \rangle^s u||_{L^p}.\]
	Decomposing the sum at the transition $N = 1$ into high and low frequencies, we conclude
		\begin{align*}
			 ||u||_{L^q} 
			 	&\lesssim \left( \sum_{N < 1} + \sum_{N \geq 1} \right) N^{\frac{d}{p} - \frac{d}{q}} ||u_N||_{L^p} \\
			 	&\lesssim \sum_{N \leq 1} N^{\frac{d}{p} - \frac{d}{q} -s} || \langle \nabla \rangle^s u||_{L^p} +  \sum_{N < 1} N^{\frac{d}{p} - \frac{d}{q}} || \langle \nabla \rangle^s u||_{L^p} \sim || \langle \nabla \rangle^s u||_{L^p},
		\end{align*}	 
	as desired. 	
\end{proof}

\subsection{$C^{0, \alpha}$-inequalities}

In the non-endpoint inequality, surplus regularity $s > \tfrac{d}{p}$ allows us to go past integrability $q = \infty$ and recover continuity. We can be more precise and show that in fact Holder continuity holds. Let $0 < \alpha < 1$, define the \emph{inhomogeneous Holder space}, $C^{0, \alpha} (\R^d)$, as the closure of Schwartz space $\cS (\R^d)$ with respect to the norm 
	\[ ||u||_{C^{0, \alpha}} := ||u||_{C^0} + \sup_{0 < |x - y| < 1} \frac{|u(x) - u(y)|}{|x - y|} ,\]
and the \emph{homogeneous Holder space}, $\dot C^{0, \alpha} (\R^d)$, as the closure of homogeneous Schwartz space $\dot \cS (\R^d)$ with respect to the norm 
	\[ ||u||_{\dot C^{0, \alpha}} := \sup_{x \neq y} \frac{|u(x) - u(y)|}{|x - y|} .\]
The Holder spaces admit the following characterisation by Littlewood-Paley projections,


\begin{proposition}[Besov characterisation of Holder norm]
	Let $0 < \alpha < 1$, then 
		\begin{align*}
			 ||u||_{C^{0, \alpha}}
			 	&\sim ||u_{\leq 1}||_{L^\infty} + \sup_{N \in 2^\N} N^\alpha ||u_N||_{L^\infty},
			 \\
			 ||u||_{\dot C^{0, \alpha}}
			 	&\sim \sup_{N \in 2^\Z} N^\alpha ||u_N||_{L^\infty}.
		\end{align*}
	The quantities on the right are known as \emph{Besov norms}. 
\end{proposition}

\begin{proof}
	As usual, we prove the homogeneous case, the inhomogeneous case is a trivial exercise. For simplicity, let us only consider the case $k = 0$. Using $\int \widecheck{\psi_N} = \psi_N (0) = 0$ and a change of variables $Ny = z$, we can write
		\begin{align*}
			u_N (x) = (u * \widecheck{\psi_N})(x) 
				&= N^d \int_{\R^d} u(x - y) \widecheck\psi (Ny) dy \\
				&= \int_{\R^d} u(x - z/N) \widecheck \psi (z) dz = \int_{\R^d} \Big( u(x - z/N) - u(x)\Big) \widecheck \psi (z) dz.
		\end{align*}	
	Taking the $L^\infty$-norm of the above, applying Minkowski's inequality and the Holder condition gives
		\begin{align*}
			||u_N||_{L^\infty} \lesssim ||u||_{\dot C^{0, \alpha}} N^{-\alpha} . 
		\end{align*}
	This proves the Holder norm controls the Besov norm. To prove the converse inequality, we decompose the difference $u(x) - u(y)$ into high and low frequencies; let $M \in 2^\Z$ satisfy $ |x - y|^{-1} \sim M$, it follows from the triangle inequality that
		\[ | u(x) - u(y)| \leq | u_{\leq M}(x) - u_{\leq M} (y)|+ | u_{\geq M}(x) - u_{\geq M} (y)|.  \]
	For the high frequency terms, we crudely estimate by the triangle inequality, 
		\[ | u_{\geq M} (x) - u_{\geq M}(y) | \lesssim \sum_{N\geq M} ||u_N||_{L^\infty} \lesssim \sup_{N \in 2^\Z} N^{\alpha} || u_N||_{L^\infty}  \sum_{N \geq M} N^{-\alpha} \sim  |x - y|^{\alpha} \sup_{N \in 2^\Z} N^\alpha || u_N||_{L^\infty}.\]	
	This furnishes the desired bound for the high frequency terms. For the low frequency terms, we can write using the fundamental theorem of calculus
		\[  u_{\leq M} (x) -  u_{\leq M} (y)  = (x - y) \cdot \int_0^1 \nabla u_{\leq M} (\theta x - (1 - \theta) y) d \theta. \]	
	Applying the triangle, Minkowski, Sobolev-Bernstein inequalities, we obtain
		\[ |u_{\leq M} (x) -  u_{\leq M} (y)| \leq |x - y| \sum_{N \leq M} ||\nabla u_{N}||_{L^\infty_x} \lesssim   |x - y|^{\alpha} \sup_{N \in 2^\Z} N^\alpha || u_N||_{L^\infty} . \]	
	This furnishes the desired bound for the low frequency terms, completing the proof. 		
\end{proof}



\begin{theorem}[Morrey's inequality]
	Let $1 < p < \infty$, then 
		\[ || u ||_{\dot C^{0, \alpha}} \lesssim |||\nabla|^s u||_{L^p}  \]
	for $0 < \alpha < 1$ satisfying $s - \tfrac{d}{p} = \alpha$. In particular, $\dot W^{s, p} (\R^d) \subseteq \dot C^{0, \alpha} (\R^d)$. Similarly for the inhomogeneous case. 
\end{theorem}

\begin{proof}
	By Sobolev-Bernstein and Bernstein's inequality, we obtain 
		\begin{align*}
			||u_N||_{L^\infty}
				&\leq N^{-s} || |\nabla|^s u||_{L^\infty} \lesssim N^{-\alpha} |||\nabla|^s u||_{L^p}.
		\end{align*}
	Rearranging and taking the supremum over $N \in 2^\Z$ completes the proof. 
\end{proof}

\subsection{Hardy-Littlewood-Sobolev inequality}

The proof of the endpoint Sobolev inequality in the spirit of that above is far more technical since we do not access to the lower order terms on the right. Furthermore, the triangle inequality and boundedness of the projections are too inefficient to be effective in the critical case. We instead follow the classical approach of \cite{Hedberg} using an inverse Sobolev inequality, namely

\begin{lemma}[Hardy-Littlewood-Sobolev inequality]
	For $u \in L^p (\R^d)$ and $1 < p, r < \infty$, we have
		\[ || |\nabla|^{-\alpha} u||_{L^r} \lesssim ||u||_{L^p} \]
	whenever $0 < \alpha < d$ and $\frac{\alpha}{d} + \tfrac1r = \tfrac1p$. At the endpoint $p = 1$, we also have the weak-type estimate
		\[ || |\nabla|^{-\alpha} u||_{L^{r, \infty}} \lesssim ||u||_{L^1}. \]
	The analogous results hold replacing $|\nabla|^{-\alpha}$ with $\langle \nabla \rangle^{-\alpha}$. 
\end{lemma}

\begin{proof}
	Without loss of generality take $||u||_{L^p} = 1$. We aim to control the convolution pointwise by the maximal function of $f$ and the $L^p$-norm of $u$. For $R > 0$ to be chosen later, 	
		\[ |(u * |x|^{\alpha - d})(x)| \leq \int_{\R^d} |x - y|^{\alpha - d} |u(y)| dy = \Big( \int_{|x - y| < R} + \int_{|x - y| \geq R} \Big)  |x - y|^{\alpha - d} u(y)| dy. \]
	Dividing the integral over the singularity into integrals over annular regions with dyadic radii, 
		\begin{align*}
			\int_{|x - y| < R}  |x - y|^{\alpha - d} |u(y)| dy 
				&\leq \sum_{r \in 2^\Z \ : \ r \lesssim R} \int_{r \leq |x - y| \leq 2r}  |x - y|^{d - \alpha} |u(y)| dy \\
				&\leq \sum_{r \in 2^\Z \ : \ r \lesssim R} r^{\alpha - d} \int_{|x - y| \leq 2r} |u(y)| dy \lesssim  \sum_{r \in 2^\Z \ : \ r \lesssim R} r^{\alpha} Mu (x) \lesssim R^{\alpha} Mu(x).
		\end{align*}	
	Applying Holder's inequality, the integral away from the singularity is controlled pointwise by
		\[  \int_{|x - y| \geq R}  |x - y|^{\alpha - d} |u(y)| dy \leq ||u||_{L^p} || |x|^{\alpha - d} ||_{L^{p'} (|x| \geq R)} \sim R^{-\frac{d}{r}}. \]
	 Choosing the optimal radius $R = Mu(x)^{-p/d}$, we obtain the pointwise bound $|(u * |x|^{\alpha - d} ) (x)| \lesssim Mu (x)^{p/r}$. Since the maximal operator is strong-type $(p, p)$, we conclude
		\[ ||u * |x|^{\alpha - d} ||_{L^r_x} \lesssim ||(Mu)^{p/r}||_{L^r} = ||Mu||^{p/r}_{L^p} \lesssim ||u||_{L^p}^{p /r} =1,  \]
	and analogously at the endpoint $p = 1$ using the weak-type $(1, 1)$ inequality. This completes the proof. 
\end{proof}

\begin{theorem}[Endpoint Sobolev inequality]
	Let $1  < p < q < \infty$, then 
		\[ ||u||_{L^q} \lesssim |||\nabla|^s u||_{L^p} \]
	whenever $\tfrac1p - \tfrac1q = \tfrac{s}{d}$ and $0 < s < \tfrac{d}{p}$. In particular, $\dot W^{s, p} (\R^d) \subseteq L^q (\R^d)$. The analogous inhomogeneous results also hold.
\end{theorem}

\begin{proof}
	By duality, Plancharel's theorem, and Holder's inequality, 
		\begin{align*}
			 ||u||_{L^q} 
			 	&= \sup_{v \in \dot \cS (\R^d) \, ; \, ||v||_{L^{q'}} = 1} \langle u, v \rangle =  \sup_{v \in \dot \cS (\R^d) \, ; \, ||v||_{L^{q'}} = 1} \langle \widehat u, \widehat v \rangle=  \sup_{v \in \dot \cS (\R^d) \, ; \, ||v||_{L^{q'}} = 1} \langle |\xi|^s \widehat u, |\xi|^{-s} \widehat v \rangle \\
			 	&\sim  \sup_{v \in \dot \cS (\R^d) \, ; \, ||v||_{L^{q'}} = 1} \langle |\nabla|^s u, |x|^{s - d} * v \rangle \leq  || |\nabla|^s u||_{L^p} \sup_{v \in \dot \cS (\R^d) \, ; \, ||v||_{L^{q'}} = 1} |||x|^{s - d} * v||_{L^{p'}}. 
		\end{align*}	 
	It follows from Hardy-Littlewood-Sobolev that
		\[ || |x|^{d - s} * v||_{L^{p'}} \lesssim ||v||_{L^{q'}} \]
	for $1 + \tfrac{1}{p'} = \tfrac{1}{q'} + \tfrac{d - s}{d}$, which, upon rearranging, is equivalent to $\tfrac1p = \tfrac1q + \tfrac{s}{d}$, completing the proof. 
\end{proof}


\begin{theorem}
	Let $1 \leq p \leq \infty$ and $\alpha > 0$, then the Bessel potential maps $L^p (\R^d)$ onto itself with operator norm $||\langle \nabla \rangle^{-\alpha}||_{L^p \to L^p} \leq 1$. In particular, for $s > 0$, we have
		\[ ||u||_{L^p} \leq || \langle \nabla \rangle^s u ||_{L^p}. \]
\end{theorem}

\begin{proof}
	The Bessel potential kernel has unit mass, so the result follows from Young's convolution inequality. The corresponding Sobolev inequality follows from duality.  
\end{proof}



